Strings functions analysis

### 2022-08-28 article.tex
method section created
results starting changed

\usepackage{rotating}
\usepackage{debate}
\usepackage{ffcode}
\usepackage{mathtools}
\usepackage{amsmath}
\usepackage{MnSymbol}
\usepackage[capitalize]{cleveref}
\usepackage{paralist}
\usepackage{cancel}
\usepackage{to-be-determined}
\usepackage{tikz}

@@

    \hl{add Section Metrics}

@@

    \subsection{Considered functions}

    In order to investigate functions, we have to make a list of functions to be investigated. We chose N languages. They were chosen based on parameters such as the number of questions on StackOverflow, the number of repositories on GitHub with 100+ stars, and the TIOBE Index; and they implement different paradigms (e.g. strict and non-strict typing). \hl{add some part of bench table}

    We should keep in mind that the number of string functions in different programming languages is very large, and this number can grow, as we said before, without limitations. For this reason, this article does not consider all existing functions, but only those that meet some criteria.

    To avoid self-repeats, a summary list of the functions to be analyzed is presented in section \ref{table 1}.

@@

    The GitHub and Sourcegraph platforms we choose to calculate the number of uses of the functions. This platform provides the ability to search for any words or phrases in all GitHub projects, as well as if necessary to specify other parameters. However, we should keep in mind that asking for the number of repetitions of a certain word in the code will in some cases not give the right result, for a number of reasons.

@@

    For some words, it is more common for them to appear in files as names/comments/inside strings rather than as called functions. Since the article deals with the use of string functions for object-oriented languages, and they use dot notation, it will be more efficient to make queries like .<function name>, instead of <function name>.

@@

    In this kind of analysis, for some functions there is a problem that it is not clear which class of objects has which function. For example, the contains function is present in string as well as in most collections.

@@

    It is worth noting that functions which have had this problem are popular, this we have obtained by making queries about the number of times they occur for code bases. For this reason, this data will not be counted in this article.

@@

    For any function (in our case string functions) we can consider such a parameter as its use by other functions. It is important because it is impossible to exclude a function from the library in case many other functions of the library use it.

@@

    \subsection{Finding the minimum set}

@@

@@

    After considering the criteria, we chose 10 programming languages. Languages such as Java, Python, C++, Ruby, JavaScript, Go, C\#, Swift, PHP, Rust were chosen.

@@

            char-at &  &  &  &  &  &  &  &  &  &  &  &  & 1 & 1 \\

>>>>

\usepackage{rotating}
\usepackage{debate}
\usepackage{tabularx}
\usepackage{ffcode}
\usepackage{mathtools}
\usepackage{amsmath}
\usepackage{MnSymbol}
\usepackage[capitalize]{cleveref}
\usepackage{paralist}
\usepackage{cancel}
\usepackage{to-be-determined}
\usepackage{tikz}

@@

@@

@@

    The GitHub and Sourcegraph platforms we choose to calculate the number of uses of the functions. This platform provides the ability to search for any words or phrases in all GitHub projects, as well as if necessary to specify other parameters. However, we should keep in mind that asking for the number of repetitions of a certain word in the code will in some cases not give the right result, for a number of reasons. \hl{maybe move platforms names to Method Section}

@@

    For some words, it is more common for them to appear in files as names/comments/inside strings rather than as called functions. Since the article deals with the use of string functions for object-oriented languages, and they use dot notation, it will be more efficient to make queries like \textit{.function}, instead of \textit{function}. \hl{to discussion}

@@

    In this kind of analysis, for some functions there is a problem that it is not clear which class of objects has which function. For example, the \textit{contains} function is present in string as well as in most collections.

@@

    It is worth noting that functions which have had this problem are popular, this we have obtained by making queries about the number of times they occur for code bases. For this reason, this data will not be counted in this article. \hl{to discussion}

@@

    For any function we can consider such a parameter as its use by other functions. It is important because it is impossible to exclude a function from the library in case many other functions of the library use it.

@@

    \subsection{The minimum set}

@@

    \hl{maybe move algorithm to Section method}

    \section{Method}

    In order to investigate functions, we will make a list of functions to be investigated. We will choose N languages. They were chosen based on parameters such as the number of questions on StackOverflow, the number of repositories on GitHub with 100+ stars, and the TIOBE Index; and they implement different paradigms (e.g. strict and non-strict typing).
    We should keep in mind that the number of string functions in different programming languages is very large, and this number can grow, as we said before, without limitations. For this reason, this article does not consider all existing functions, but only those that meet some criteria.

@@

    Below are the 10 programming languages we have chosen and their criteria.

    \hl{Java, Python, C++, Ruby, JavaScript, Go, C\#, Swift, PHP, Rust were chosen.}

@@

            Get \textbf{char-at} a given position &  &  &  &  &  &  &  &  &  &  &  &  & 1 & 1 \\
